---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo      = TRUE,
  eval      = FALSE,
  collapse  = TRUE,
  comment   = "#>",
  fig.path  = "man/figures/README-",
  out.width = "100%"
)
modulesHome <- file.path("", "opt", "local", "share", "Modules")
```

# RLinuxModules

<!-- badges: start -->
[![R build status](https://github.com/kiwiroy/RLinuxModules/workflows/R-CMD-check-basic/badge.svg)](https://github.com/kiwiroy/RLinuxModules/actions)
<!-- badges: end -->

R package that makes linux [environment modules](http://modules.sourceforge.net/) available from R.

## Installation

<s>You can install the released version of RLinuxModules from [CRAN](https://CRAN.R-project.org) with:</s>

``` r
# Not released to CRAN
# install.packages("RLinuxModules")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kiwiroy/RLinuxModules@main")
```
## Example

This is a basic example which shows you how to solve a common problem when using environment modules with R:

```{r example}
library(RLinuxModules)

# initialise
moduleInit(modulesHome = modulesHome)

# load samtools into the environment
module("load samtools") 

# samtools should now be available
system("samtools", intern = TRUE)
```

While in a knitr code chunk using `bash` as the engine.
```{r bash-chunk, engine = "bash"}
# Environment is inherited in other code chunks.
which samtools
```

```{r module-loading, engine = "bash"}
# see known issues below
module list
```

## How it works
 
The Modules Environment now supports R scripting since version 4.0. <s>This package works by using the python support and translating the python commands returned from *modulecmd python* into R commands. It has only been tested for version 3.2.10</s>

### Known issues

1. If `/bin/sh` is symlinked to `/bin/dash`, `dash` will sanitize the environment in such a way that the `module` function is not available to the child `bash` shell. See a [bug report](https://bugs.debian.org/cgi-bin/bugreport.cgi?bug=814358) and [Stack Overflow question](https://stackoverflow.com/q/38079864) on the topic.
